---
title: "p8105_hw1_sl4660"
author: "Sibei Liu"
date: "2019/9/14"
output: github_document
---

# Problem 1

```{r,message = FALSE}
library(tidyverse)
 first_df=tibble(
   norm_samp=rnorm(8),
   norm_samp_log = norm_samp > 0,
   char_vec=c("a","b","c","d","e","f","g","h"),
   factor_vec=factor(c("1","2","3","1","2","3","1","2")),
 )
 
mean(pull(first_df,norm_samp))
mean(pull(first_df,norm_samp_log))
mean(pull(first_df,char_vec))
mean(pull(first_df,factor_vec))
```

Next, let's use `as.numeric` function to change variables

```{r}
 norm_samp_log2=as.numeric(pull(first_df,norm_samp_log))
 char_vec2=as.numeric(pull(first_df,char_vec))
 mean_factor_vec2=as.numeric(pull(first_df,factor_vec))
```

And multiply them with random sample

```{r}
pull(first_df,norm_samp)*norm_samp_log2
norm_samp_log3=factor(pull(first_df,norm_samp_log))
pull(first_df,norm_samp)*norm_samp_log3
norm_samp_log4=as.numeric(norm_samp_log3)
pull(first_df,norm_samp)*norm_samp_log4
```

# Problem 2

```{r}
  second_df=tibble(
    x=rnorm(500),
    y=rnorm(500),
    log_vec=x+y>1,
    nu_vec=c(as.numeric(log_vec)),
    fac_vec=factor(log_vec),
  )
```

the row number of `second_df` dataset is `r nrow(second_df)` and the colum number of `second_df` is `r ncol(second_df)` 

the mean, median and standered deviation of `x` are `r mean(pull(second_df,x))`, `r median(pull(second_df,x))` and `r sd(pull(second_df,x))` respectively

 the proportion of cases for which `x+y>1` is `r (length(which(pull(second_df,log_vec)==TRUE)))/nrow(second_df)`
 
```{r}
ggplot(second_df,aes(x=x,y=y,color=log_vec))+geom_point()
ggsave("hw1_plot1.pdf", height = 4, width = 6)
ggplot(second_df,aes(x=x,y=y,color=nu_vec)) + geom_point()
ggplot(second_df,aes(x=x,y=y,color=fac_vec))+geom_point()
```